\documentclass[12pt, twoside]{report}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,width=150mm,top=25mm,bottom=25mm,bindingoffset=6mm]{geometry}
\usepackage{graphicx}
\usepackage[backend=bibtex, style=authoryear]{biblatex}
\addbibresource{references.bib}


\begin{document}

\input{Titlepage/titlepage}

\chapter*{Abstract}
Always do this one last, when knowing the things to praise  yourself for :P

\chapter*{Acknowledgements}
If I don't profit from nice people in these thesis, I have done something horrible wrong. So try to remember most of them here at the end... :)

\tableofcontents

% \listoffigures

% \listoftables

\chapter{Introduction}
\parencite{surveyOfTextMining}

The introduction points out, what this thesis is about, why it is actual usefull and finishes with an overview of the structure of this thesis.

\section{What is this thesis about?}
This thesis deals with the topic of making ingredients of recipes within a cookbook machine-readable.

Extracting information from textual resources is a new field of research. In contrast to KDD the information are unstructed, what make it really hard to automatically extract usefull information. For example the world wide web is actual  a

\textbf{Text mining} was first mentioned in \parencite{KDT}


here text mining
recipe parsing problem 
structured prediction problem 



\textbf{Structure of this thesis:} ...
\section{Why is this relevant?}
Beside that the previous decripted topic is very interesting from a computer science view, it can also help in many practical points.

relevant cause of data minig:
	already: Kochbuch.de...
	Zukunft Gesellschaft, Geschichte...


\section{Structure of this thesis}

\chapter{Theory basics}
\section{Machine-readable data}
\section{Machine learning}
\section{Exact formulation of the problem}
\section{Similar work}



\appendix
\chapter{Statutory Declaration}
\input{Appendix/appendix}

\chapter{Something else}
hi

\chapter{Something else else}
hello

\printbibliography

\end{document}